Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-05 paper.tex
modified a definition
make small change in a definition

\begin{definition}
	Let $|\widehat{t}\rangle$ denote $t$ represented in unary. That is, a state of the form $|11\ldots1\rangle |00\ldots0\rangle$; that is, $t$ $1$s followed by all $0$s.
\end{definition}

@@

\begin{definition}
	A \emph{quantum delegation protocol} is an polynomial-round interactive protocol between a BPP verifier and a possibly malicious BQP prover. The BPP verifier has an arbitrary quantum circuit with classical input. Its goal is to evaluate the quantum circuit with an honest prover.
\end{definition}

>>>>

\begin{definition}
	Let $|\widehat{t}\rangle=|11\ldots1\rangle |00\ldots0\rangle$; $t$ $1$s followed by all $0$s. $t$ represented in unary.
\end{definition}

@@

\begin{definition}
	A \emph{quantum delegation protocol} is an polynomial-round interactive protocol between a BPP verifier and a BQP prover. The BPP verifier has an arbitrary quantum circuit with classical input that it needs to evaluate with the help of the prover.
\end{definition}
